Supplemental Information B: Full Annotated Analysis and Reproducible Code

### 2021-10-14 Supplemental-Material-B-Annotated-Analysis.Rmd
worker att-keyneed added

# Install and Load Packages
# !IMPORTANT!
# BEFORE FIRST RENDER:
# To install all relevant packages please run "renv::restore()" (or renv::init() and then initiate from lockfile) in the console before the first use to ensure that all packages are using the correct version.
# to store the packages in a contained library within the project folder: renv::settings$use.cache(FALSE) and add 'RENV_CONFIG_SANDBOX_ENABLED = FALSE' to an '.Renviron' file 
lib <- c("rmarkdown", "knitr", "remedy", "bookdown", "psych",
         "ggplot2", "ggthemes", "haven", "RColorBrewer", "plotly", "gridExtra", "ggpattern",
         "lme4", "nlme", "jtools",
         "sessioninfo", "tibble", "pander", "devtools", "mada",
         "data.table", "plyr", "dplyr", "tidyr", "Hmisc", "kableExtra", "papaja",
         "stringr", "stringi", "reshape2", "lubridate")
invisible(lapply(lib, library, character.only = TRUE))  
rm(lib)

@@

@@

@@

>>>>

# Install and Load Packages
# !IMPORTANT!
# BEFORE FIRST RENDER:
# To install all relevant packages please run "renv::restore()" (or renv::init() and then initiate from lockfile) in the console before the first use to ensure that all packages are using the correct version.
# to store the packages in a contained library within the project folder: renv::settings$use.cache(FALSE) and add 'RENV_CONFIG_SANDBOX_ENABLED = FALSE' to an '.Renviron' file 
lib <- c("rmarkdown", "knitr", "remedy", "bookdown", "psych",
         "ggplot2", "ggthemes", "haven", "RColorBrewer", "plotly", "gridExtra", "ggpattern",
         "lme4", "nlme", "jtools", "gtsummary",
         "sessioninfo", "tibble", "pander", "devtools", "mada",
         "data.table", "plyr", "dplyr", "tidyr", "Hmisc", "kableExtra", "papaja",
         "stringr", "stringi", "reshape2", "lubridate")
invisible(lapply(lib, library, character.only = TRUE))  
rm(lib)

@@

make a model with only the data but a random intercept (unconditional model) for the outgroup interaction subset.

```{r workerOutPrep}
# see how large our outgroup interaction subset actually is 
tbl_cross(workerInteractionType, row=OutgroupInteraction, col=NonOutgroupInteraction, percent="row")

# create outgroup interaction subset
workerOutgroupInteraction <- workerInteractionType %>%
  filter(OutgroupInteraction == "Yes")
```

\begin{equation}
(\#eq:WorkerOutEmptyModel)
Attitude_{ti} = \gamma_{00} + u_{0i} + e_{ti} \\
\textrm{with}\ u_{0i} \sim \mathcal{N}(0,\tau_{00}^2)\ \textrm{and}\ e_{ti} \sim \mathcal{N}(0,\sigma^2)
\end{equation}

```{r Worker.Out.Null.Model.ML}
# Create and save Model
  Null.Out.ML.r = lme4::lmer(thermometerDutch_1~1 + (1|PID),data=workerOutgroupInteraction) #use optim if it does not converge
  Null.Out.ML = lme(thermometerDutch_1~1,random=~1|PID, data=workerOutgroupInteraction, control=list(opt="nlmimb")) #use optim if it does not converge

# Get summary with p-values (Satterthwaite's method)
  #summary(Null.ML.r) #or with the lme function
  summ(Null.Out.ML.r, digits = 3, center = TRUE)

# Save variances
  v.out.null <- VarCorr(Null.Out.ML) # save variances
# The estimate of (between-group or Intercept variance, tau_{00}^2):
  tau <- as.numeric(v.out.null[1])
# and the estimate of (within-group or residual variancel, sigma^2) is:
  sigma <- as.numeric(v.out.null[2])
# The ICC estimate (between/between+within) is:
  ICC <- (as.numeric(v.out.null[1])/(as.numeric(v.out.null[1])+as.numeric(v.out.null[2])))
  ICC.Perc <- ((as.numeric(v.out.null[1])/(as.numeric(v.out.null[1])+as.numeric(v.out.null[2]))))*100
```

@@

```{r interceptAttKeyNeed}
# Create and save Model
  model.keyneed = lme(thermometerDutch_1 ~ keymotive_fulfillemt_1, random=~1|PID,data=workerOutgroupInteraction)

# Get summary with p-values (Satterthwaite's method)
  summ(lmer(thermometerDutch_1 ~ keymotive_fulfillemt_1 + (1|PID),data=workerOutgroupInteraction), 
       confint = TRUE, digits = 3, center = TRUE)

# Compare new model to previous step
  anova(Null.Out.ML, model.keyneed) %>%
    as.data.frame %>%
    select(-call) %>%
    kbl(., 
        #label = "",
        caption = "Worker: Model Comparison",
        format = "html", 
        linesep = "",
        booktabs = T,
        align = rep('c', ncol(.)),
        digits = 3)  %>%
  kable_styling(position = "left")

# Save variances
  v.keyneed <- lme4::VarCorr(model.keyneed)

# The estimate of between-group (or Intercept variance) explained: 
  # Variance Explained = 1 – (Var with Predictor/Var without Predictor)
    v.keyneed.btw <- 1 - (as.numeric(v.keyneed[1])/as.numeric(v.out.null[1]))
    v.keyneed.btw.perc <-  (1 - (as.numeric(v.keyneed[1])/as.numeric(v.out.null[1])))*100
  # and the estimate of within-group (or residual variancel) explained is:
    v.keyneed.within <- 1 - (as.numeric(v.keyneed[2])/as.numeric(v.out.null[2]))
    v.keyneed.within.perc <- (1 - (as.numeric(v.keyneed[2])/as.numeric(v.out.null[2])))*100
```

@@

```{r slopesAttKeyNeed}
# Create and save Model (optimizer needed to reach convergence)
  model.keyneed.ran = lme(thermometerDutch_1~
                         keymotive_fulfillemt_1, 
                         random=~1+keymotive_fulfillemt_1|PID,
                       control=lmeControl(opt='optim'), data=workerOutgroupInteraction)

# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
  summ(model.keyneed.ran0 <- lmer(thermometerDutch_1 ~
                           keymotive_fulfillemt_1 + 
                           (1+keymotive_fulfillemt_1|PID), 
                         data=workerOutgroupInteraction), 
       confint = TRUE, digits = 3, center = TRUE)

# Compare new model to previous step
  anova(model.keyneed, model.keyneed.ran) %>%
    as.data.frame %>%
    select(-call) %>%
    kbl(., 
        #label = "",
        caption = "Worker: Model Comparison",
        format = "html", 
        linesep = "",
        booktabs = T,
        align = rep('c', ncol(.)),
        digits = 3)  %>%
  kable_styling(position = "left")

# Save variances
  v.keyneed.ran = lme4::VarCorr(model.keyneed.ran)

# The estimate of between-group (or Intercept variance) explained: 
  # Variance Explained = 1 – (Var with Predictor/Var without Predictor)
    v.keyneed.ran.btw <- 1 - (as.numeric(v.keyneed.ran[1])/as.numeric(v.keyneed[1]))
    v.keyneed.ran.btw.perc <-  (1 - (as.numeric(v.keyneed.ran[1])/as.numeric(v.keyneed[1])))*100
  # and the estimate of within-group (or residual variancel) explained is:
    v.keyneed.ran.within <- 1 - (as.numeric(v.keyneed.ran[2])/as.numeric(v.keyneed[2]))
    v.keyneed.ran.within.perc <- (1 - (as.numeric(v.keyneed.ran[2])/as.numeric(v.keyneed[2])))*100

# Assumption Checks: 
  diag = sjPlot::plot_model(model.keyneed.ran0, type = "diag")
  grid.arrange(diag[[1]],diag[[2]]$`PID`,diag[[3]],diag[[4]])

# Plot prediction model
  dat.new = workerOutgroupInteraction[,c("thermometerDutch_1","session","PID")]
  dat.new$measure = predict(model.keyneed.ran, workerOutgroupInteraction, re.form=NA)

  (t.ppt = ggplot(data=dat.new, aes(x=session, y=measure)) + 
    geom_line(alpha=1, color = "blue") +
    geom_line(aes(y = thermometerDutch_1), alpha=1)+
    facet_wrap(~PID, ncol = 6)+
    xlab("Time")+
    ylab("Outgroup Attitudes")+
    theme_bw())
  ggsave(filename = "Figures/Development per PPT Out Keyneed.png", t.ppt,
       width = 18, height = 12, dpi = 800, units = "cm", device='png')
